Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-21 4_methodology/methodology.tex
no message

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. Since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. With this aim, each mismatch pattern and its analyzers are defined by extending the following definitions:
\theoremstyle{definition}
    \begin{definition}
    Mismatch Pattern is a tuple ${Mismatch\ Patten} = (O_{1}, O_{2}, ExtensionData, A_{start}, A_{end}) $ where 
    \begin{enumerate}
      \item $O_{1}$ is the first organization and \item $O_{2}$ is the second organization in between the pattern occurs,
      \item $ExtensionData$ is a set of tuples where mismatch related information is recorded, 
      \item $A_{start}$ and $A_{end}$ are starting and ending points to check mismatch patterns.
    \end{enumerate}
    \end{definition}
\theoremstyle{definition}

@@

For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
  \caption{Mismatch Pattern Analysis Stage as Black-box}
  \label{fig:mismatch-pattern-analysis-blackbox}
\end{figure}

>>>>

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. Since performance indicators are calculated based on a starting and ending point in the process model, the same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. With this aim, each mismatch pattern and its analyzers are defined by extending the following definitions. For each organization, mismatch pattern analyzers are pipelined and mismatch patterns are stored for further analysis.
\theoremstyle{definition}
    \begin{definition}
    Mismatch Pattern is a tuple ${Mismatch\ Patten} = (O_{1}, O_{2}, ExtensionData, A_{start}, A_{end}) $ where 
    \begin{enumerate}
      \item $O_{1}$ is the first organization and \item $O_{2}$ is the second organization in between the pattern occurs,
      \item $ExtensionData$ is a set of tuples where mismatch related information is recorded, 
      \item $A_{start}$ and $A_{end}$ are starting and ending points to check mismatch patterns.
    \end{enumerate}
    \end{definition}
\theoremstyle{definition}

@@
